The first high-redshift Changing Look Quasars

### 2019-11-07 tex/other_tex/201909/CIV_notes_20190920.tex
CIV tex/ tidy up

Samples of over 100 ``Changing Look'' quasars (CLQs) or ``Changing State'' quasars (CSQs) have now been 
assembled \citep[e.g.][]{MacLeod2019, Graham2019}. The community uses both these
terms as a cover for the underlying physics. For sake of argument, ``Changing Look'' quasars can be 
thought of as the extension of ``regular'' quasar variability \citep[e.g.][]{MacLeod2012} whereas 
the ``Changing State'' quasars (CSQs) have a `state-transition' similar to that in Galactic X-ray binaries
\citep[e.g][]{NodaDone2018, Ruan2019}. 
%
These CLQs have primarily been defined according to the (recombination) Balmer emission line properties with 
particular attention paid to the H$\beta$ emission line, usually observed from optical spectroscopy. 
As such, current CLQ studies have been at redshifts $z<1$.

While there have been a slew of studies on triply ionized carbon, i.e
\civ, these have tended to focus on broad absorption line quasars
\citep[BAL QSOs; see e.g. Table 1][]{Hemler2019} or the Baldwin Effect
\citep[BEff; e.g. ][]{Baldwin1977, Bian2012, Jensen2016,
Hamann2017}\footnote{As noted in \citet{Rakic2017}, two different
types of Baldwin effect are present in the literature: the {\it
global} (or {\it ensemble}) Baldwin Effect, which is an anti-correlation
between the EW of the emission line and the underlying continuum
luminosity of {\it single-epoch} observations of a {\it large number}
of AGN and second, the {\it intrinsic} Baldwin effect, the same anti-correlation
but in an {\it individual, variable} AGN \citep{PoggePeterson1992}.}.
%%
Dramatic changes in the collisionally excited  broad {\it emission} line (BEL) 
of \civ (and indeed \ciii) have not to this point been seen.

Here, we report on three quasars  
%SDSS J120544.7+342252.4  (hereafter J1205+3422), 
%SDSS J163852.93+282707.7 (hereafter J1638+2827) and
%SDSS J222818.76+220102.9 (hereafter J2228+2201)  
which show dramatic changes in their \civ\ and \ciii broad emission line
properties as well as in the underlying continuum. We claim these are
the first examples of ``Changing Look Quasars'' at high ($z>1$)
redshift. Moreover, these are cases for dramatic changes of 
ions with high ionization potentials (I.P.'s $>$2 Rydberg).

%%
In this paper we use the wavelengths of 1548.202 and 1550.774 \AA\ for the \civ doublet
%Example of how to reference these results:
using the values from the National Institute of Standards and Technology (NIST) Atomic Spectra Database 
\citep{Kramida2018}. 
% A., Ralchenko, Yu., Reader, J., and NIST ASD Team (2018). NIST Atomic Spectra Database (ver. 5.6.1), [Online]. Available: https://physics.nist.gov/asd [2019, September 17]. National Institute of Standards and Technology, Gaithersburg, MD. DOI: https://doi.org/10.18434/T4W30F

%The singly ionized hydrogen atom H+ is referred to as HII, doubly ionized oxygen O++ is called OIII, etc.

%“24.4 eV is energy needed for C I to get rid of two electrons, and become doubly-ionised C III”
%% https://en.wikipedia.org/wiki/Ionization_energies_of_the_elements_(data_page)
The ground state of carbon is 1$s^2$ 2$s^2$ 2$p^2$.
Using the \href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST Atomic Spectra Database Ionization Energies Form}
for ionisation energies, we see 
11.3 eV is the energy needed for C I to dislodge one electron and become singly-ionised C II; 
24.4 eV is energy needed for singly-ionised C II to dislodge an additional electron, and become doubly-ionised C III, 
and 47.89 eV  (3.519 Ry) is required for doubly-ionised C III  become triply--ionised \civ. 
64.49 eV (4.74 Ry) is the energy needed to ionize \civ itself.

The 1548.202 	and 1550.774 \AA\ emission doublet is created by the 
2$p$ $^{2}P_{0}$ $---$  2$s$ $^{2}S$ transition with 
energies 64,484 cm$^{-1}$ and 64591 cm$^{-1}$ 
\citep[e.g.][]{Moore1993}.

Ground  Shells:  1$s^{2}$2$s$. 
Ground  Level: $^{2}S_{1/2}$. 
Ionized  Level: 1$s^{2}$ $^{1}S_{0}$.

\subsection{Literature Search}
\citet{Gregory1982} reported time variability in both Lya and \civ 1550 emission lines in the Seyfert galaxy NGC 5548.

From \citet{VandenBerk2001} 
The rest positions of emission lines in quasar spectra, especially the
high-ionization broad lines, are known to vary from their nominal
laboratory wavelengths \citep{Gaskell1982, Wilkes1986,  Espey1989, Espey1990Erratum, 
ZhengSulentic1990, Corbin1990, Weymann1991, TytlerFan1992, 
Brotherton1994, Laor1995, McIntosh1999}.

\citet{Wilhite2006} examine the variability of the high-ionizaton
C~\textsc{iv}$\lambda{1549}$ line in a sample of 105 quasars observed
at multiple epochs by the Sloan Digital Sky Survey.  We find a strong
correlation between the change in the C~\textsc{iv} line flux and the
change in the line width, but no correlations between the change in
flux and changes in line center and skewness.  The relation between
line flux change and line width change is consistent with a model in
which a broad line base varies with greater amplitude than the line
core. The objects studied here are more luminous and at higher
redshift than those normally studied for variability, ranging in
redshift from 1.65 to 4.00 and in absolute $r$-band magnitude from
roughly $-$24 to $-$28.  Using moment analysis line-fitting
techniques, we measure line fluxes, centers, widths and skewnesses for
the C~\textsc{iv} line at two epochs for each object.  The well-known
Baldwin Effect is seen for these objects, with a slope $\beta =
-0.22$.  The sample has a median intrinsic Baldwin Effect slope of
$\beta_{int} = -0.85$; the C~\textsc{iv} lines in these
high-luminosity quasars appear to be less responsive to continuum
variations than those in lower luminosity AGN.  Additionally, we find
no evidence for variability of the well known blueshift of the
C~\textsc{iv} line with respect to the low-ionization
Mg~\textsc{ii}$\lambda$2798 line in the highest flux objects,
indicating that this blueshift might be useful as a measure of
orientation.

%% NAZAROVA 2003
%% BROAD EMISSION LINES La, C IV AND Hb IN NGC 5548
%% Astronomical and Astrophysical Transactions
%% Vol. 22, Nos. 4–5, August–October 2003, pp. 681–689

@@

\citet{Denney2015}, 
%Denney, Kelly; SDSS-RM Team, ``The Effects of S/N on Measuring CIV Broad Emission Line Widths in Quasars - An Early Science Result from the Sloan Digital Sky Survey Reverberation Mapping Project'' ; http://adsabs.harvard.edu/abs/2015AAS...22520403D
The Sloan Digital Sky Survey Reverberation Mapping (SDSS-RM) Project
spectroscopically monitored $\sim$850 quasars over a seven square
degree field for approximately six months with the BOSS
spectrograph. While the time series analysis of the quasar continuum
and emission-line variability, and thereby the potential to measure
reverberation time delays from this sample, is still underway, we have
used the subset (roughly half) of this sample containing the \civ 1549\AA 
broad emission line to investigate the effects of S/N on measuring
this broad emission line width. Line width measurements are necessary
for inferring the broad line region gas velocities used to determine
the quasar black hole mass. However, literature studies have suggested
line width measurements, and therefore black hole mass estimates, may
be biased by the use of relatively low S/N, typical survey-quality,
data, compared to the high S/N data that calibrate single-epoch black
hole mass scaling relations. The SDSS-RM data set provides a unique
opportunity to search for any systematic uncertainties in CIV line
width measurements through a comparison of line widths measured from
the single-epoch spectra, which are roughly equivalent to other
SDSS/BOSS quasar spectra (though still twice the exposure time) to
those measured from the high-S/N, campaign co-added spectra, which
contain more than 30 epochs of each source. Here we present results
from this investigation, which have implications for estimating CIV
single-epoch black hole masses from the SDSS/BOSS and other surveys.

%% Coatman et al. (2017, AAS; http://adsabs.harvard.edu/abs/2017AAS...22930203C) 
%%Accurate black-hole (BH) mass estimates for high-redshift (z>2) quasars are essential for better understanding the relationship between super-massive BH accretion and star formation. Progress is currently limited by the large systematic errors in virial BH-masses derived from the CIV broad emission line, which is often significantly blueshifted relative to systemic, most likely due to outflowing gas in the quasar broad-line region. We have assembled Balmer-line based BHmasses for a large sample of 230 high-luminosity (1045.5-1048 ergs-1), redshift 1.5<z<4 quasars, which, for the first time, span the entire range of CIV blueshifts seen in the quasar population. We find the CIV-based BH-masses to be larger than the corresponding Balmer line-based masses by almost an order of magnitude at the most extreme blueshifts (˜5000 kms-1). An empirical correction to the CIV BH-masses is derived, which depends only on the properties of the CIV line itself (i.e. blueshift and FWHM). 
%%
\citet{Coatman2017AAS} show that this new correction now enables the derivation of un-biased CIV-based virial BH masses for the majority of high-luminosity, high-redshift quasars.In the same high-luminosity quasar sample, we find the narrow [OIII] emission to be weaker and more asymmetric than is generally found in  lower-luminosity AGN and that a significant fraction of our quasars have exceptionally broad (FWHM $> 3000 km s^{-1}$), blueshifted [OIII] emission. We find a strong correlation between the \civ and [OIII] blueshifts. This correlation holds even for quasars at fixed
luminosity and suggests that broad line region outflows in quasars are
connected to galaxy-scale winds.

\citet{Coatman2016} show that at high redshift, $z>2.1$, black hole
masses are normally derived using the velocity width of the C IV
$\lambda \lambda$1548, 1550 broad emission line, based on the
assumption that the observed velocity widths arise from virial-
induced motions. In many quasars, the \civ emission line exhibits
significant blue asymmetries  with the line centroid
displaced by up to thousands of km s$^{-1}$ to the blue. These blueshifts
almost certainly signal the presence of strong outflows, most likely
originating in a disc wind. We have obtained near-infrared spectra,
including the H$\alpha$ $\lambda$6565 emission line, for 19 luminous 
(L$_{\rm Bol} =46.5–47.5$ erg s$^{-1}$) Sloan Digital Sky Survey quasars, at redshifts $2 <
z < 2.7$, with \civ emission lines spanning the full range of
blueshifts present in the population. A strong correlation between C
IV velocity width and blueshift is found and, at large blueshifts,
$>$2000 km s$−1$, the velocity widths appear to be dominated by non-virial
motions. Black hole masses, based on the full width at half-maximum of
the \civ emission line, can be overestimated by a factor of 5 at large
blueshifts. A larger sample of quasar spectra with both \civ and H$\beta$, 
or H$\alpha$, emission lines will allow quantitative corrections to \civ-based black hole masses as a function of blueshift to be
derived. We find that quasars with large \civ blueshifts possess high
Eddington luminosity ratios and that the fraction of high-blueshift
quasars in a flux-limited sample is enhanced by a factor of
approximately 4 relative to a sample limited by black hole mass.

%% \citet{Coatman2017} 
The \civ $\lambda \lambda$1498,1501 broad emission line is visible in optical spectra to redshifts exceeding $z\sim5$. \civ has long been known to exhibit significant displacements to the blue and these `blueshifts' almost certainly signal the presence of strong outflows. As a consequence, single-epoch virial black hole (BH) mass estimates derived from \civ velocity widths are known to be systematically biased compared to masses from the hydrogen Balmer lines. 
\citet{Coatman2017} use a large sample of 230 high-luminosity (LBol = 1045.5-1048 erg s-1), redshift $1.5 < z < 4.0$ quasars with both \civ and Balmer line spectra, we have quantified the bias in \civ BH masses as a function of the \civ blueshift. \civ BH masses are shown to be a factor of 5 larger than the corresponding Balmer-line masses at C IV blueshifts of 3000 km s-1 and are overestimated by almost an order of magnitude at the most extreme blueshifts, $\gtrsim$5000 km s$^{-1}$. Using the monotonically increasing relationship between the \civ blueshift and the mass ratio BH(\civ)/BH(H$\alpha$), we derive an empirical correction to all C IV BH masses. The scatter between the corrected C IV masses and the Balmer masses is 0.24 dex at low C IV blueshifts ($\sim$0 km s-1) and just 0.10 dex at high blueshifts ($\sim$3000 km s$^{-1}$), compared to 0.40 dex before the correction. The correction depends only on the C IV line properties - i.e. full width at half-maximum and blueshift - and can therefore be applied to all quasars where C IV emission line properties have been measured, enabling the derivation of unbiased virial BH-mass estimates for the majority of high-luminosity, high-redshift, spectroscopically confirmed quasars in the literature.

\citet{Sun2018} use the multi-epoch spectra of 362 quasars from the Sloan Digital Sky Survey Reverberation Mapping project to investigate the dependence of the blueshift of \civ relative to \mgii on quasar properties. We confirm that high-blueshift sources tend to have low \civ equivalent widths (EWs), and that the low-EW sources span a range of blueshift. Other high-ionization lines, such as He II, also show similar blueshift properties. The ratio of the line width (measured as both the full width at half maximum and the velocity dispersion) of \civ to that of \mgii increases with blueshift. Quasar variability enhances the connection between the \civ blueshift and quasar properties (e.g., EW). The variability of the \mgii line center (i.e., the wavelength that bisects the cumulative line flux) increases with blueshift. In contrast, the C IV line center shows weaker variability at the extreme blueshifts. Quasars with the high-blueshift \civ lines tend to have less variable continuum emission, when controlling for EW, luminosity, and redshift. Our results support the scenario that high-blueshift sources tend to have large Eddington ratios.

\citet{Richards2011} 
use a sample of $\sim$30,000 quasars from the 7th Data Release of the Sloan Digital Sky Survey, and explore the range of properties exhibited by high-ionization, broad emission lines, such as \civ $\lambda$1549. Specifically, we investigate the anti-correlation between continuum luminosity and emission-line equivalent width (the Baldwin Effect (BEff)) and the ``blueshifting''of the high-ionization emission lines with respect to low-ionization emission lines. 
%Employing improved redshift determinations from Hewett \& Wild, the blueshift of the C IV emission line is found to be nearly ubiquitous, with a mean shift of ~810 km s-1 for radio-quiet (RQ) quasars and ~360 km s-1 for radio-loud (RL) quasars. The BEff is present in both RQ and RL samples. We consider these phenomena within the context of an accretion disk-wind model that is modulated by the nonlinear correlation between ultraviolet and X-ray continuum luminosity. Composite spectra are constructed as a function of C IV emission-line properties in an attempt to reveal empirical relationships between different line species and the continuum. Within a two-component disk+wind model of the broad emission-line region (BELR), where the wind filters the continuum seen by the disk component, we find that RL quasars are consistent with being dominated by the disk component, while broad absorption line quasars are consistent with being dominated by the wind component. Some RQ objects have emission-line features similar to RL quasars; they may simply have insufficient black hole (BH) spin to form radio jets. Our results suggest that there could be significant systematic errors in the determination of L bol and BH mass that make it difficult to place these findings in a more physical context. 
It is possible to classify quasars in a paradigm where the diversity of BELR parameters is due to differences in an accretion disk wind between quasars (and over time); these differences are underlain primarily by the spectral energy distribution, which ultimately must be tied to BH mass and accretion rate.

Also from \citet{Richards2011}, 
At high redshift, two well-known properties of the Civ emission line are evident in quasar spectra (see Section 4). An anti-correlation between luminosity and the equivalent width (EQW) of C iv, generally known as the Baldwin Effect (BEff; Baldwin 1977), was first identified in 20 (mostly radio-loud (RL)) quasars and has been confirmed in much larger samples (e.g., Wu et al. 2009). The other effect is the blueshifting of the C iv with respect to the systemic redshift (Gaskell 1982; Wilkes 1984). As with the BEff, these blueshifts have not only been confirmed with larger samples, but appear to be nearly ubiquitous in the quasar population (Sulentic et al. 2000b; Richards et al. 2002a).

%\includegraphics\includegraphics[]{../../../../../Users/npr1/Downloads/Richards_2011_AJ_141_167.pdf}

%\citet{1994}
%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ApJ___425__622P.pdf}

%\citet{1994}
%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ASPC___69____1P.pdf}

\citet{Denney2016}
%\includegraphics[]{../../../../../Users/npr1/Downloads/Denney_2016_ApJS_224_14.pdf}
investigate the dependence on data quality of quasar properties
measured from the C IV emission line region at high redshifts.  Our
measurements come from 32 epochs of Sloan Digital Sky Survey
Reverberation Mapping Project spectroscopic observations of 482 $z >
1.46$ quasars. We compare the differences between measurements made
from the single-epoch (SE) and coadded spectra, focusing on the \civ
$\lambda$1549 emission line because of its importance for studies of
high-redshift quasar demographics and physical properties, including
black hole masses. In addition to statistical errors increasing (by
factors of $\sim2-4$), we find increasing systematic offsets with
decreasing signal-to-noise ratio (S/N).

\citet{Grier2015}....
%\includegraphics[]{../../../../../Users/npr1/Downloads/Grier_2015_ApJ_806_111.pdf}

\citep{Corbin1991, Dimitrijevic1992, Wills1993, Brotherton1994, Osmer1994} ...

\citep{Nazarova2003} ...

%\includegraphics[]{../../../../../Users/npr1/Downloads/Misawa_2007_ApJ_660_152.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/Punsly_2010_ApJ_713_232.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/Sun_2015_ApJ_811_42.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/Joshi_2019_ApJ_871_43.pdf}

Recent investigations also include \citet{Meyer2019}.

\iffalse
\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/J2228+2201.png}
  \vspace{-12pt}
  \caption[]{J222818.7+220102.6. 
% EMERGING., 
The light curve shows it brightening from 20.5 to 19.5 over the 771 days observed-frame between the two SDSS spectra available. 
A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] emerging on a new blue contiuum slope.}
  \label{fig:disk_suppression}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/J1638+2827.png}
  \vspace{-12pt}
  \caption[]{The quasar SDSS J163852.9+282708. 
% Disappearing 
A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] fading.}
  \label{fig:disk_suppression}
\end{figure}
\fi

>>>>

Samples of over 100 ``Changing Look'' quasars (CLQs) or ``Changing
State'' quasars (CSQs) have now been assembled
\citep[e.g.][]{MacLeod2019, Graham2019}. The community uses both these
terms as a cover for the underlying physics. For sake of argument,
``Changing Look'' quasars can be thought of as the extension of
``regular'' quasar variability \citep[e.g.][]{MacLeod2012} whereas the
``Changing State'' quasars (CSQs) have a `state-transition' similar to
that in Galactic X-ray binaries \citep[e.g][]{NodaDone2018, Ruan2019}.
These CLQs have primarily been defined according to the
(recombination) Balmer emission line properties with particular
attention paid to the H$\beta$ emission line, usually observed from
optical spectroscopy.  As such, current CLQ studies have been at
redshifts $z<1$.

While there have been a slew of studies on triply ionized carbon, i.e
\civ, these have tended to focus on broad absorption line quasars
\citep[BAL QSOs; see e.g. Table 1][]{Hemler2019} or the Baldwin Effect
\citep[BEff; e.g. ][]{Baldwin1977, Bian2012, Jensen2016,
Hamann2017}\footnote{As noted in \citet{Rakic2017}, two different
types of Baldwin effect are present in the literature: the {\it
global} (or {\it ensemble}) Baldwin Effect, which is an
anti-correlation between the EW of the emission line and the
underlying continuum luminosity of {\it single-epoch} observations of
a {\it large number} of AGN and second, the {\it intrinsic} Baldwin
effect, the same anti-correlation but in an {\it individual, variable}
AGN \citep{PoggePeterson1992}.}.  Dramatic changes in the
collisionally excited broad {\it emission} line (BEL) of \civ (and
indeed \ciii) have not to this point been seen.

Here, we report on three quasars  
%SDSS J120544.7+342252.4  (hereafter J1205+3422), 
%SDSS J163852.93+282707.7 (hereafter J1638+2827) and
%SDSS J222818.76+220102.9 (hereafter J2228+2201)  
which show dramatic changes in their \civ\ and \ciii broad emission
line properties as well as in the underlying continuum. We claim these
are the first examples of ``Changing Look Quasars'' at high ($z>1$)
redshift. Moreover, these are the first cases for substantial changes
of ions with high ionization potentials (I.P.'s $>$2 Rydberg), thus
linking the ionizing photons to the energetic inner accretion disk,
potentially by inverse Compton scattering lower energy photons to
higher energies.  Furthermore, the measured rest-wavelengths of
emission lines in quasar spectra, are known to vary from their nominal
laboratory especially for the high-ionization broad lines,
wavelengths, \citep[e.g.][]{VandenBerk2001}.

In this paper we use the wavelengths of 1548.202 and 1550.774 \AA\ for
the \civ doublet \citep{Kramida2018}.
%%  The singly ionized hydrogen atom H+ is referred to as HII, doubly ionized oxygen O++ is called OIII, etc.
%%  “24.4 eV is energy needed for C I to get rid of two electrons, and become doubly-ionised C III”
%%  https://en.wikipedia.org/wiki/Ionization_energies_of_the_elements_(data_page)
The ground state of carbon is 1$s^2$ 2$s^2$ 2$p^2$.  Using the
\href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST
Atomic Spectra Database Ionization Energies Form} for ionisation
energies, we see 11.3 eV is the energy needed for C I to dislodge one
electron and become singly-ionised C II; 24.4 eV is energy needed for
singly-ionised C II to dislodge an additional electron, and become
doubly-ionised C III, and 47.89 eV (3.519 Ry) is required for
doubly-ionised C III become triply--ionised \civ.  64.49 eV (4.74 Ry)
is the energy needed to ionize \civ itself.
%%
The 1548.202 and 1550.774 \AA\ emission doublet is created by the 2$p$
$^{2}P_{0}$ $---$ 2$s$ $^{2}S$ transition with energies 64,484
cm$^{-1}$ and 64591 cm$^{-1}$ \citep[e.g.][]{Moore1993}.
%Ground  Shells:  1$s^{2}$2$s$. 
%Ground  Level: $^{2}S_{1/2}$. 
%Ionized  Level: 1$s^{2}$ $^{1}S_{0}$.

%%\subsection{Literature Search}
\civ\ variability has been long studied, \citep[e.g., ][]{Baldwin1977,
Gaskell1982, Gregory1982, Wilkes1986, Espey1989, Espey1990Erratum,
ZhengSulentic1990, Corbin1990, Corbin1991, Weymann1991,
Dimitrijevic1992, TytlerFan1992, Wills1993, Brotherton1994, Osmer1994,
Laor1995, McIntosh1999}.
%%
%\citet{Gregory1982} reported time variability in both Lya and \civ 1550 emission lines in the Seyfert galaxy NGC 5548.
%
%\citet{1994}
%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ASPC___69____1P.pdf}

%% NAZAROVA 2003
%% BROAD EMISSION LINES La, C IV AND Hb IN NGC 5548
%% Astronomical and Astrophysical Transactions
%% Vol. 22, Nos. 4–5, August–October 2003, pp. 681–689
\citep{Nazarova2003} ...

\citet{Wilhite2006} examine the variability of a C~\textsc{iv} 
sample of 105 quasars observed at multiple epochs by the SDSS. 
They find a strong correlation between the change in the C~\textsc{iv} line flux and the
change in the line width, but no correlations between the change in 
flux and changes in line center and skewness.  These authors find 
that the relation between line flux change and line width change is consistent with a model in
which a broad line base varies with greater amplitude than the line
core. The C~\textsc{iv} lines in these 
high-luminosity quasars appear to be less responsive to continuum
variations than those in lower luminosity AGN.  
%% Additionally, we find no evidence for variability of the well known
blueshift of the C~\textsc{iv} line with respect to the low-ionization
Mg~\textsc{ii}$\lambda$2798 line in the highest flux objects,
indicating that this blueshift might be useful as a measure of
orientation.

@@

\citet{Richards2011} explored the BELR in over 30,000 $z > 1.54$ SDSS
quasars, concentrating on the properties of the \civ\ emission
line. We consider two well-known effects involving the \civ\ emission
line: the anti-correlation between the \civ\ EQW and luminosity (i.e.,
the BEff) and the blueshifting of the peak of \civ\ emission with
respect to the systemic redshift. These authors conclude that these
two \civ\ parameters (EQW and blueshift) are capturing an important
trade-off between ``disk'' and ``wind'' components in the disk-wind
model of accretion disks \citep[e.g.,][]{Murray1995, Elvis2000, Proga2000}.  with one dominating over the other depending on the
shape of the SED \citep[][]{Leighly2004b}.  (strong \civ EQW indicates
a more ionizing SED and large \civ blueshift indicating a less
ionizing SED).

%% \citet{Grier2015}....
%% \includegraphics[]{../../../../../Users/npr1/Downloads/Grier_2015_ApJ_806_111.pdf}
%% \citet{Denney2015}, 
%%Denney, Kelly; SDSS-RM Team, ``The Effects of S/N on Measuring CIV Broad Emission Line Widths in Quasars - An Early Science Result from the Sloan Digital Sky Survey Reverberation Mapping Project'' ; http://adsabs.harvard.edu/abs/2015AAS...22520403D
The Sloan Digital Sky Survey Reverberation Mapping (SDSS-RM) Project 
\citep{Shen2015} has a  monitored $\sim$350 quasars with \civ
Noting the biases associated with \civ Emission Line Properties 
\citep[e.g. increasing systematic offsets with decreasing signal-to-noise][]{Denney2016}, 
\citet{Grier2019} report 
report significant time delays between the continuum and the CIV 1549 emission line in 52 quasars, 
and investigate the \civ radius-luminosity relationship.

%% \citet{Coatman2017} 
%The \civ $\lambda \lambda$1498,1501 broad emission line is visible in optical spectra to redshifts exceeding $z\sim5$. 
\civ has long been known to exhibit significant displacements to the blue and these `blueshifts' almost certainly signal the presence of strong outflows. As a consequence, single-epoch virial black hole (BH) mass estimates derived from \civ velocity widths are known to be systematically biased compared to masses from the hydrogen Balmer lines. 
\citet{Coatman2017} use a large sample of 230 high-luminosity (LBol = 1045.5-1048 erg s-1), redshift $1.5 < z < 4.0$ quasars with both \civ and Balmer line spectra, we have quantified the bias in \civ BH masses as a function of the \civ blueshift. \civ BH masses are shown to be a factor of 5 larger than the corresponding Balmer-line masses at C IV blueshifts of 3000 km s$^{-1}1$ and are overestimated by almost an order of magnitude at the most extreme blueshifts, $\gtrsim$5000 km s$^{-1}$. 
%Using the monotonically increasing relationship between the \civ blueshift and the mass ratio BH(\civ)/BH(H$\alpha$), we derive an empirical correction to all C IV BH masses. The scatter between the corrected C IV masses and the Balmer masses is 0.24 dex at low C IV blueshifts ($\sim$0 km s-1) and just 0.10 dex at high blueshifts ($\sim$3000 km s$^{-1}$), compared to 0.40 dex before the correction. The correction depends only on the C IV line properties - i.e. full width at half-maximum and blueshift - and can therefore be applied to all quasars where C IV emission line properties have been measured, enabling the derivation of unbiased virial BH-mass estimates for the majority of high-luminosity, high-redshift, spectroscopically confirmed quasars in the literature.

\citet{Sun2018} use the multi-epoch spectra of 362 quasars from the Sloan Digital Sky Survey Reverberation Mapping project to investigate the dependence of the blueshift of \civ relative to \mgii on quasar properties. We confirm that high-blueshift sources tend to have low \civ equivalent widths (EWs), and that the low-EW sources span a range of blueshift. Other high-ionization lines, such as He II, also show similar blueshift properties. The ratio of the line width (measured as both the full width at half maximum and the velocity dispersion) of \civ to that of \mgii increases with blueshift. Quasar variability enhances the connection between the \civ blueshift and quasar properties (e.g., EW). The variability of the \mgii line center (i.e., the wavelength that bisects the cumulative line flux) increases with blueshift. In contrast, the C IV line center shows weaker variability at the extreme blueshifts. Quasars with the high-blueshift \civ lines tend to have less variable continuum emission, when controlling for EW, luminosity, and redshift. Our results support the scenario that high-blueshift sources tend to have large Eddington ratios.
%%
Therefore, the \civ\ or \heii\ EW is not an accurate indicator of the Eddington ratio or quasar SED.
%%
Recent investigations also include \citet{Meyer2019}.

This paper is organised as follows. In Section 2, we describe our
sample selection, catalogs and observationa data sets.  In Section 3,
we present various theoretical models and discuss if and how each
describes and explains the data.  We conclude in Section 4.  We report
all magnitudes on the AB zero-point system \citep{Oke_Gunn1983,
Fukugita1996} unless otherwise stated explicitly. For the WISE bands,
$m_{\rm AB} = m_{\rm Vega} + m$ where $m = (2.699, 3.339)$ for WISE W1
at 3.4$\mu$m and WISE W2 at 4.6$\mu$m, respectively
\citep{Cutri2011}. We choose the cosmological parameters
$\Omega_{\Lambda} = 0.7$, $\Omega_{\rm M} = 0.3$, and $h = 0.7$ in
order to be consistent with \citet{Shen2011}.
